Sexual dimorphism in trait variability and its eco-evolutionary

### 2020-11-19 scripts/MouseSexDiffVar_Oct_2020.Rmd

overall4.female.sigS <- overall4.female.sigS %>%
                          mutate(value = as.numeric(value),
                                 ci.low = as.numeric(ci.low),
                                 ci.high = as.numeric(ci.low))

@@

# end combination Figure 5
FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.5, 2.2, 2.1, 2), labels = c("A", " ", "B", " "))
FigS2
ggsave("Figure4_2.pdf", plot = FigS2, width = 6, height = 7)
```

>>>>

overall4.female.sigS <- overall4.female.sigS %>%
                          mutate(value = as.numeric(value),
                                 ci.low = as.numeric(ci.low),
                                 ci.high = as.numeric(ci.high))

@@

# end combination Figure 5
FigS2 <- ggarrange(malebias_FigS2_sigtraits, malebias_Fig2_over10, FigS2b, FigS2d, ncol = 1, nrow = 4, heights = c(2.5, 2.2, 2.1, 2), labels = c("A", " ", "B", " "))
FigS2
ggsave("Figure4_2.pdf", plot = FigS2, width = 8, height = 9)
```
